---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "figures/README-",
  out.width = "100%"
)
```
# psyphr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/psyphr)](https://cran.r-project.org/package=psyphr)
<!-- badges: end -->

The `psyphr` R package tranforms [psychophysiological](https://en.wikipedia.org/wiki/Psychophysiology) data from 
commercial data collection and processing systems into a [tidy](http://vita.had.co.nz/papers/tidy-data.pdf) form for downstream analysis and visualization.

### WIP 

The package is currently under active development. 

Currently, the package supports data outputs from the the following corresponding [MindWare Technologies](https://www.mindwaretech.com/) applications in version 3.2: 

- [Electrodermal Activity (EDA)](https://support.mindwaretech.com/manuals/software/eda/3-2/)
- [Heart Rate Variability (HRV)](https://support.mindwaretech.com/manuals/software/hrv/3-2/) 
- [Electromyography (EMG)](https://support.mindwaretech.com/manuals/software/emg/3-2/)
- [Blood Pressure Variability (BPV)](https://support.mindwaretech.com/manuals/software/bpv/3-2/)
- [Impedance Cardiography (IMP)](https://support.mindwaretech.com/manuals/software/imp/3-2/)
- <del>[Basic Signal Analysis (BSA)](https://support.mindwaretech.com/manuals/software/bsa/3-2/)</del>(No support currently)


## Installation

Install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("wendtke/psyphr")
```
## Usage

Load and attach `psyphr`.

```{r eval = FALSE}
require(psyphr)
```


### Read a Single File

### Compile a Study

#### Directory Structure

### Exploratory Analysis


## TODO

The development team considers the following for the package's future:

- Submit `psyphr` to [rOpenSci](https://ropensci.org/) for peer review and publication
- Customizable data QA utilities with meaningful defaults
- Common, publication-grade visualization schemes
- Study compilation utility
- Compatibility on data feeds from other popular data collection and processing systems (e.g., [BIOPAC](https://www.biopac.com/))

## Acknowledgements

`psyphr` was founded at the [Uncoast Unconf 2019](https://github.com/uncoast-unconf/uu-2019) with the help of [Amanda Gadrow](https://github.com/ajmcoqui) and [Audrey McCombs](https://github.com/almccombs). 

This material is based upon work supported by the National Science Foundation Graduate Research Fellowship Program under Grant No. 006784-00002 [to KEW]. Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the views of the National Science Foundation.

